Rising from the Ashes II: The Bar-driven Abundance Bimodality of the Milky Way

### 2025-02-28 paper/ms.tex
Update Micic citation

There is a significant body of theoretical and observational work in support of this picture. Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}. It was recently shown by \citet{2024arXiv240906783F} that bars can induce quiescence by accelerating the growth of a SMBH, but they found there can be many Gyr between bar formation and quenching. In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.\footnote{\citet{2022A&A...668L...3L} studied a galaxy from TNG100 in which a merger induced AGN activity that ejected gas from its center. A bar then formed out of the gas-poor disk.} Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.

>>>>

There is a significant body of theoretical and observational work in support of this picture. Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}. It was recently shown by \citet{2024arXiv240906783F} that bars can induce quiescence by accelerating the growth of a SMBH, but they found there can be many Gyr between bar formation and quenching. In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.\footnote{\citet{2022A&A...668L...3L} studied a galaxy from TNG100 in which a merger induced AGN activity that ejected gas from its center. A bar then formed out of the gas-poor disk.} Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024ApJ...968L..21M,2024Natur.630...54B}.
